Amazonian Narratives in Presidential Discourse (1985 to 2020)

### 2021-11-08 08112021_Sposito_and_SilvaMuller_DRAFT.Rmd
#added text to plots #formatted markdown so HTML or pdf look a bit nicer

# Fit a simple LDA model
# Please note that we randomly set a K = 10 (10 cluster = topics)
amazon_lda <- topicmodels::LDA(amazon_dtm, k = 10, control = list(seed = 1234))

>>>>

# Fit a simple LDA model
# Please note that we randomly set a K = 10 (10 cluster = topics)

amazon_dtm  <- DocumentTermMatrix(amazon_corpus)
amazon_dtmm <- as.matrix(amazon_dtm)
amazon_lda <- topicmodels::LDA(amazon_dtm, k = 10, control = list(seed = 1234))
